### 2016-03-09 paper/algorithm.tex
yasu

\section{Multi-way particle swarm fusion}
Multi-way Particle Swarm Fusion is a natural extension of Fusion Move
method (FM). We call our method Swarm Fusion (SF) in short. Take a
multi-threading environment to explain our idea, while the technique is
also applicable to other parallel programming model such as {\it
MapReduce} in cloud computing.
%

Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$, each thread
$T_i$ maintains and updates a solution $S_i$ in parallel. Alpha
expansion picks one label in each iteration to perform fusion. FM
invokes one proposal generation scheme and generates a solution proposal
for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we
pick arbitrary number of proposal generation schemes and generate
proposals, and 2) a {\it solution pool}, from which we pick arbitrary
number of intermediate solutions generated by all the other threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread.

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
thread $T_i$), determining the processing flow of the algorithm: In each
fusion step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool, following
a user-defined strategy or at random to be simple.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.
Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods. mention
 that hierarchical fusion works in a different way, but we can still
 consider that to be our special case, by letting each thread not using
 its own solution in the next fusion.}\label{fig:model}
\end{figure}
%
The bottom right configuration is the most general one, in which we
always fuse some solution proposals and some concurrent solutions
(i.e., $\alpha\ne 0, \beta \ne 0$).
%
Each fusion is multi-way (not binary) with a non-submodular energy, and
we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
inference techniques can be used~\cite{opengm}. Of course, if one knows
that a certain fusion step is a binary fusion with submodular energy,
one can use graph-cuts instead~\cite{alpha_expansion_paper}. If a
certain fusion step is a binary fusion with non-submodular energy, one
can use QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

\mysubsubsubsection{Relationships to existing methods}

\noindent It is easy to verify that alpha-expansion
(AE)~\cite{alpha_expansion}, fusion move (FM)~\cite{viktor}, parallel
alpha-expansion (PAE)~\cite{delong}, and hierarchical fusion
(HF)~\cite{delong_hierarchical,olga} are all special cases of the Swarm
Fusion method.~\footnote{The hierarchical fusion has a slightly
different data processing model, without strong ties between threads
data, but this can be considered as a special case of SF by not using
$S_i$ in each fusion step of $T_i$.} For example, AE can be realized by
setting $\alpha=1, \beta=0$ and restricting the proposal generation to
constant labels with a single thread. Same goes for FM, this time,
without the restriction on the proposal generation scheme. PAE is
realized by setting $\alpha=1,\beta=1$ with multiple threads, again with
a restriction on the proposal generation scheme. The last sequential
fusion (at the top of the diagram in the figure) can be modeled by
changing to $\alpha=0, \beta=1$ with a single thread.

>>>>

\section{Multi-way particle swarm fusion}
Multi-way Particle Swarm Fusion is a natural extension of Fusion Move
method (FM). We call our method Swarm Fusion (SF) in short. Let us take
a multi-threading environment to explain our idea, while the technique
is also applicable to other parallel programming model such as {\it
MapReduce} in cloud computing.
%

Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$, each thread
$T_i$ maintains and updates a solution $S_i$ in parallel. Alpha
expansion picks one label in each iteration to perform fusion. FM
invokes one proposal generation scheme and generates a solution proposal
for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we
pick arbitrary number of proposal generation schemes and generate
proposals, and 2) a {\it solution pool}, from which we pick arbitrary
number of intermediate solutions generated by the other threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers the solution
from each thread.

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
thread $T_i$), determining the processing flow of the algorithm: In each
fusion step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool, based on a
user-defined strategy or at random to be simple.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.
Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods. The
 bottom right example shows the general Swarm fusion architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The framework is flexible and
 can realize other data processing architectures depending on the parameters.
 %
 % The left two examples at the
 % bottom row are other Swarm fusion architectures with some restrictions,
 % for which we provide comparative evaluations in
 % Section~\ref{section:results}.
 %
 The left two examples at the bottom are other Swarm fusion
 architectures with some restrictions, to be used for evaluations later.
 %
 It is also easy to verify that existing methods such as
 alpha-expansion~\cite{alpha_expansion}, Fusion move~\cite{FM}, parallel
 alpha-expansion~\cite{delong}, or hierarchical
 fusion~\cite{delong_hierarchical_fusion,olga}, are all special
 cases of the Swarm fusion.}\label{fig:model}
\end{figure}
%
The bottom right architecture is the most general one, in which we
always fuse some solution proposals and some concurrent solutions (i.e.,
$\alpha\ne 0, \beta \ne 0$).
%
Each fusion is multi-way (not binary) with a non-submodular energy, and
we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
inference techniques can be used~\cite{opengm}. For instance, if one
knows that a certain fusion step is a binary fusion with submodular
energy, one can use graph-cuts~\cite{alpha_expansion_paper}. If a
certain fusion step is a binary fusion with non-submodular energy, one
can use QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

\mysubsubsection{Relationships to existing methods}

\noindent It is easy to verify that alpha-expansion
(AE)~\cite{alpha_expansion}, fusion move (FM)~\cite{viktor}, parallel
alpha-expansion (PAE)~\cite{delong}, and hierarchical fusion
(HF)~\cite{delong_hierarchical,olga} are all special cases of the Swarm
Fusion method. AE can be realized by setting $(\alpha=1, \beta=0)$ and
restricting the proposal generation to constant labels with a single
thread. Same goes for FM, this time, without the restriction on the
proposal generation scheme. PAE is realized by setting
$(\alpha=1,\beta=1)$ with multiple threads, again with a restriction on
the proposal generation scheme (the last sequential fusion in PAE is
realized by $(\alpha=0, \beta=1)$ with a single thread).
%
% The last sequential fusion (at the top of the example in the figure) can
% be modeled by changing to $\alpha=0, \beta=1$ with a single thread.
HF has a slightly different data processing model, without strong ties
between threads and data, but can be realized by setting ($\alpha=2,
\beta=0$) at the bottom level and ($\alpha=0, \beta=2$) at the remaining
levels, while allowing $S_i$ not to be used in the fusion steps of
$T_i$.
